Proposal to improve BBC Search through the use of Linked Data

### 2014-05-20 chapter4.1.tex
Done! Reviewed and ready to submit.

\begin{figure}
  \begin{center}
\begin{dot2tex}[dot,scale=0.55]
digraph ingest {
  rankdir=TB;

@@

An abstract overview of the flow of content is given in figure~\ref{led-indexing-chain}.
As with the current system depicted in figure~\ref{indexing-chain},
there remains an ``Ingest'' API to which any system may
send content to be indexed if it has already been transformed to
use the semantics required by the search application. This
ensures that integration work done by other teams continues to work
and retains the use case where content producers wish to have full
control of what metadata is sent to the search indexed -- as long as
they are willing to do the integration work.

@@

The URLNotification service can generate a minimal RDF graph and the
rest of the indexing chain can be seen as a process that incrementally
augments this graph until it is suitable for indexing and has sufficient
information to display search results. It is proposed that these minimal
graphs will take the form of the following example (in JSON-LD serialisation):

\begin{centering}
\begin{lstlisting}[language=json]
[
  {
    "@id": "http://www.bbc.co.uk/news/technology-27346567",
    "http://purl.org/dc/terms/identifier": [
      {
        "@value": "http://www.bbc.co.uk/news/technology-27346567"
      }
    ]
  }
]
\end{lstlisting}
\end{centering}

This single triple, whilst arguably tautological, can serve as a stub
for the series of augmentations further downstream. The next stage,
the \emph{URLFetch} stage, is
the attempt to add semantic metadata found by dereferencing the URL
given. This step should retrieve metadata similar to the graphs depicted
in chapter~\ref{analysis} such as figure~\ref{keepod}. If the identifier
in the stub RDF graph sent to this stage is a URI, but not a URL, then
dereferencing is not possible, but the \emph{URLFetch} stage could
passively send the graph onwards without augmenting to it.

@@

The URLFetch service can then send the augmented graph onwards to
the \emph{Enrichment} service. The purpose of this stage is to apply
any number of business rules to add further metadata to the graph
that has not been obtainable via the public website or further upstream. It is
in this service that the search team is doing more classical
\emph{enterprise integration} work, which is unavoidable, but confined
to this one service (or collection of microservices).

In the Enrichment service, we might, for example, contact backend
service applications for futher data about the content we are trying to ingest.
This might mean fetching information about a programme from services
behind BBC iPlayer or contacting content management systems for
non-published metadata about articles, videos, etc.

@@

Whilst the enrichment stage means we have not fully eliminated the
need for bespoke integration work, the important factor to consider is that
such integration is no longer \emph{required}. If basic properties
are sourced upstream from the public web page, then the lack
of ability to integration -- or if that integration breaks, as brittle,
coupled integration applications are prone to do -- then the information
can still be passed through to retain a \emph{degraded} search
experience. This is preferable to the complete loss of an upstream feed
due to incompatible changes being made unannounced.

The next stage is to run the RDF graph through an \emph{Inference} process.
This is where custom rules are invoked to handle the different
vocabularies that might be in use. For example, the rule shown below
(in N3 format) would allow us to infer that we can
use \texttt{schema:headline} anywhere we have used \texttt{rnews:headline}
or \texttt{og:title}.

\begin{centering}
\begin{lstlisting}[language=ttl]
@prefix schema: <http://schema.org/> .
@prefix rnews: <http://iptc.org/std/rNews/2011-10-07#> .
@prefix og: <http://ogp.me/ns#> .

@@

This is useful if the decision is made to use the Schema.org vocabulary as
the standard within the search indexes and application, but upstream
content from BBC News is using \texttt{rnews:headline} instead. It is this
mixed used of vocabularies that was a major driver in historic
enterprise integration efforts. In bespoke integration applications, explicit
transformation would be used to translated  ``news item'' to a
``search item'' including the rule that explicitly extracted the
\texttt{rnews:headline} property and set it on the \texttt{schema:headline}
property on the new ``search item'' being created.

In the proposed approach, the RDF model provides a generic framework where
transformation does not need to occur at any syntactic level and we
can use resuable inference rules to make more blanket statements such as
``Where the title has been set for Facebook's Open Graph, use the same
thing for the title on search results''. This rule can then apply to \emph{all}
content that uses that property without regard to what ``kind'' of content item
it is.

This may sound too open to problems where properties are miused in
unexpected ways and that inferring information in key vocabularies from
ones used by other systems might allow for ``dirty data'' to appear. Such
difficulties with the variable quality of linked data on the wider semantic
web were certainly encountered by Hogan et al.\cite{hogan2011searching} when
building the SWSE: the Semantic Web Search Engine. It is argued however,
that these risks are substantially lower for linked enterprise data as
the domain is far more controlled than the public web. It is also an important
feature of the web (both the document web and the semantic web) that linking and
decentralisation bring overall maintainability and interoperability benefits
that outweigh minor integrity concerns that organisations tradtionally attempt
to prevent with strict, controlled vocabularies, governance and bespoke
software integration.

This proposal argues it is more beneficial to take a more agile approach
of validating some minimum requirements of the information before it
enters the search indexes themselves. Any content that is not thus
being accepted can be flagged so that the rules can be amended. For example,
it might be decided that the \texttt{rnews:headline} property is only
correctly used by BBC News and other content producers use it incorrectly. In
this case, we can update our rules as shown below:

\begin{centering}
\begin{lstlisting}[language=ttl]
@prefix schema: <http://schema.org/> .
@prefix rnews: <http://iptc.org/std/rNews/2011-10-07#> .
@prefix og: <http://ogp.me/ns#> .

@@

The final stage after this inference is to push the RDF graph in
an appropriate hypermedia type such as JSON-LD to the Ingest API. At this
point, we should have all required fields/properties for indexing as
well as other properties that came from upstream sources that will not
immediately be used. It should be the r\^ole of the Ingest API to perform
some \emph{contextual validation}\cite{fowler2005contextual} to ensure
it can be indexed. Ones that cannot be indexed should be stored, but
not indexed, so there is opportunity to retrieve and repush items through
the Enrichment and Inference stages again if needed.

>>>>

\begin{figure}[t]
  \begin{center}
\begin{dot2tex}[dot,scale=0.55]
digraph ingest {
  rankdir=TB;

@@

An abstract overview of the flow of content is given in figure~\ref{led-indexing-chain}.
As with the current system depicted in figure~\ref{indexing-chain},
there remains an ``Ingest'' API to which any system may
send content to be indexed if it has already been transformed to
use the semantics required by the search application. This
ensures that integration work done by other teams continues to work
and retains the use case where content producers wish to have full
control of what metadata is sent to the search indexes -- as long as
they are willing to do the integration work.

@@

The URLNotification service can generate a minimal RDF graph and the
rest of the indexing chain can be seen as a process that incrementally
augments this graph until it is suitable for indexing and has sufficient
information to display search results. It is proposed that these minimal
graphs will take the form of the example (in JSON-LD serialisation)
shown in listing~\ref{lst:minimal}.

\begin{centering}
\begin{lstlisting}[language=json,label=lst:minimal,caption=Minimal RDF graph in JSON-LD showing only that something exists and a single identifier for it.]
{
  "@id": "http://www.bbc.co.uk/news/technology-27346567",
  "http://purl.org/dc/terms/identifier": {
    "@value": "http://www.bbc.co.uk/news/technology-27346567"
  }
}
\end{lstlisting}
\end{centering}

This single triple, whilst arguably tautological, can serve as a stub
for the series of augmentations further downstream. The next stage,
the \emph{URLFetch} stage, is
the attempt to add semantic metadata found by dereferencing the URL
given. This step should retrieve metadata similar to the graphs depicted
in chapter~\ref{analysis} such as figure~\ref{keepod}. If the identifier
in the stub RDF graph sent to this stage is a URI, but not a URL, then
dereferencing is not possible, but the \emph{URLFetch} stage could
passively send the graph onward without augmenting to it.

@@

The URLFetch service can then send the augmented graph onward to
the \emph{Enrichment} service. The purpose of this stage is to apply
any number of business rules to add further metadata to the graph
that has not been obtainable via the public website or further upstream. It is
in this service that the search team is doing more classical
\emph{enterprise integration} work, which is unavoidable, but confined
to this one service (or collection of microservices).

In the Enrichment service, we might, for example, contact back-end
service applications for further data about the content we are trying to ingest.
This might mean fetching information about a programme from services
behind BBC iPlayer or contacting content management systems for
non-published metadata about articles, videos, etc.

@@

Whilst the enrichment stage means we have not fully eliminated the
need for bespoke integration work, the important factor to consider is that
such integration is no longer \emph{required}. If basic properties
are sourced upstream from the public web page, then the lack
of ability to integrate -- or if that integration breaks, as brittle,
coupled integration applications are prone to do -- then the information
can still be passed through to retain a \emph{degraded} search
experience. This is preferable to the complete loss of an upstream feed
due to incompatible changes being made unannounced.

The next stage is to run the RDF graph through an \emph{Inference} process.
This is where custom rules are invoked to handle the different
vocabularies that might be in use. For example, the rule shown in
listing~\ref{lst:headline-rules}
(in N3 format) would allow us to infer that we can
use \texttt{schema:headline} anywhere we have used \texttt{rnews:headline}
or \texttt{og:title}.

\begin{centering}
\begin{lstlisting}[language=ttl,label=lst:headline-rules,caption=Simple inference rules to derive a suitable headline from two different vocabularies.]
@prefix schema: <http://schema.org/> .
@prefix rnews: <http://iptc.org/std/rNews/2011-10-07#> .
@prefix og: <http://ogp.me/ns#> .

@@

This is useful if the decision is made to use the Schema.org vocabulary as
the standard within the search indexes and application, but upstream
content from BBC News is using \texttt{rnews:headline} instead. It is this
mixed used of vocabularies that was a major driver in historic
enterprise integration efforts. In bespoke integration applications, explicit
transformation would be used to translate a ``news item'' to a
``search item'' including the rule that explicitly extracted the
\texttt{rnews:headline} property and set it on the \texttt{schema:headline}
property on the new ``search item'' being created.

In the proposed approach, the RDF model provides a generic framework where
transformation does not need to occur at any syntactic level and we
can use reusable inference rules to make more blanket statements such as
``Where the title has been set for Facebook's Open Graph, use the same
thing for the title on search results''. This rule can then apply to \emph{all}
content that uses that property without regard to what ``kind'' of content item
it is.

This may sound too open to problems where properties are misused in
unexpected ways and that inferring information in key vocabularies from
ones used by other systems might allow for ``dirty data'' to appear. Such
difficulties with the variable quality of linked data on the wider semantic
web were certainly encountered by Hogan et al.\cite{hogan2011searching} when
building the SWSE: the Semantic Web Search Engine. It is argued however,
that these risks are substantially lower for linked enterprise data as
the domain is far more controlled than the public web. It is also an important
feature of the web (both the document web and the semantic web) that linking and
decentralisation bring overall maintainability and interoperability benefits
that outweigh minor integrity concerns that organisations traditionally attempt
to prevent with strict, controlled vocabularies, governance and bespoke
software integration.

This proposal argues it is more beneficial to take a more agile approach
of validating some minimum requirements of the information before it
enters the search indexes themselves. Any content that is not thus
being accepted can be flagged so that the rules can be amended. For example,
it might be decided that the \texttt{rnews:headline} property is only
correctly used by BBC News and other content producers use it incorrectly. In
this case, we can update our rules as shown in listing~\ref{lst:headline-strict}.

\begin{centering}
\begin{lstlisting}[language=ttl,label=lst:headline-strict,caption=Inference rules where \texttt{rnews:headline} is only used for the headline for content from BBC News.]
@prefix schema: <http://schema.org/> .
@prefix rnews: <http://iptc.org/std/rNews/2011-10-07#> .
@prefix og: <http://ogp.me/ns#> .

@@

The final stage after this inference is to push the RDF graph in
an appropriate hypermedia type such as JSON-LD to the Ingest API. At this
point, we should have all required fields/properties for indexing as
well as other properties that came from upstream sources that will not
immediately be used. It should be the r\^ole of the Ingest API to perform
some \emph{contextual validation}\cite{fowler2005contextual} to ensure
it can be indexed. Ones that cannot be indexed should be stored, but
not indexed, so there is opportunity to retrieve and re-push items through
the Enrichment and Inference stages again if needed.

### 2014-05-20 chapter4.2.tex
Done! Reviewed and ready to submit.

The overall information architecture, design and user experience of
the results page are out of scope for this proposal, but it is likely
there could be some improvements in this area, particulary around making
the web page itself responsive\cite{marcotte2010responsive}. A separate
study might consider reviewing the use cases of BBC Search from
the viewpoint of website visitors and consider the relevant
\emph{search modes} and \emph{mode chains}, which could lead to
an information architecture that would drive metadata requirements.

>>>>

The overall information architecture, design and user experience of
the results page are out of scope for this proposal, but it is likely
there could be some improvements in this area, particularly around making
the web page itself responsive\cite{marcotte2010responsive}. A separate
study might consider reviewing the use cases of BBC Search from
the viewpoint of website visitors and consider the relevant
\emph{search modes} and \emph{mode chains}\cite{russell2012designing},
which could lead to
an information architecture that would drive metadata requirements.

### 2014-05-20 chapter4.3.tex
Done! Reviewed and ready to submit.

Editorial staff might publish assertions such as
``person $X$ is notable for $Y$'' or
``programme $X$ is a big name brand for the BBC'' and then
properties such as \texttt{foaf:homepage}\cite{brickley2012foaf} or
\texttt{po:microsite}\cite{raimond2009bbc} indicate the canonical
``home pages'' for those entities. The search application can
then index all entities that have such editorial interest marked
against them alongside their home pages and provide an
Editor's Choice feature that uses the combined strengths
of automated and manual curation.

>>>>

Editorial staff might publish assertions such as
``person $X$ is notable for $Y$'' or
``programme $X$ is a big-name brand for the BBC'' and then
properties such as \texttt{foaf:homepage}\cite{brickley2012foaf} or
\texttt{po:microsite}\cite{raimond2009bbc} indicate the canonical
``home pages'' for those entities. The search application can
then index all entities that have such editorial interest marked
against them alongside their home pages and provide an
Editor's Choice feature that uses the combined strengths
of automated and manual curation.

### 2014-05-20 chapter5.1.tex
Done! Reviewed and ready to submit.

Whilst most of the proposals in chapter~\ref{ch:proposal} were
technical in nature, most Agile practices encourage phrasing
improvements in terms of changes a user or stakeholder would see
and attach some measure of business value to them. Thus the proposed
improvements around indexing linked data, semantically-driven rich
snippets and semi-automated editorial curation are expressed as
the follow tangible improvments:

@@

\item \textbf{A programme's microsite should always be the top result.}
  In a purely-organic search, it
  is possible that news articles, etc. might contain the same keywords as a programme (e.g. some programm
  titles are incredibly generic, such as \emph{Today} on BBC Radio 4) and those results might conceivably
  be scored more highly. The Editor's Choice feature ensures the programme's microsite is always at
  the top, but with this feature we can migrate the manual curation of these programmes links to
  the proposed, automated system and reduce the need to manually manage this subset of curated links.

>>>>

Whilst most of the proposals in chapter~\ref{ch:proposal} were
technical in nature, most Agile practices encourage phrasing
improvements in terms of changes a user or stakeholder would see
and attach some measure of business value to them. Thus the proposed
improvements around indexing linked data, semantically-driven rich
snippets and semi-automated editorial curation are expressed as
the follow tangible improvements:

@@

\item \textbf{A programme's microsite should always be the top result.}
  In a purely-organic search, it
  is possible that news articles, etc. might contain the same keywords as a programme (e.g. some programme
  titles are incredibly generic, such as \emph{Today} on BBC Radio 4) and those results might conceivably
  be scored more highly. The Editor's Choice feature ensures the programme's microsite is always at
  the top, but with this feature we can migrate the manual curation of these programmes links to
  the proposed, automated system and reduce the need to manually manage this subset of curated links.

### 2014-05-20 chapter5.2.tex
Done! Reviewed and ready to submit.

As depicted in figure~\ref{led-indexing-chain}, the architectural
approach is based around discrete, decoupled, RESTful services
forming a conceptual pipeline that takes notification of content
through a process of augmentation, validation and indexing. Recognising
and exploting Conway's Law\cite{conway1968committees}, a good strategy
would be to focus subteams on each major area of the application
(so that the team organisation fits the architecture rather than the
architecture emerging from the team structure).

@@

\begin{itemize}
  \item \textbf{Discovery.} This subteam will focus on the URLNotification
    and URLFetch services as well as any integration work upstream to
    generate notifications where such mechanisms do not already exist for certain
    types of content. Typical considerions will be around RSS/Atom feeds that
    might notify of new content, message-based notifications from other
    systems and maintaining a crawler that finds the rest.
  \item \textbf{Enrichment and Inference.} Here the development team will focus
    on integration with BBC or external data sources to enrich information
    coming from the discovery stages. The developers will also need
    to gain sufficient domain knowledge of each content area to make sound
    inferences from the enriched metadata that then generate sensible
    values for fields required by the search indexes.
  \item \textbf{Ingest.} The Ingest API and the search indexes themselves
    will be maintained by a subteam responsible for accepting, validating,
    archiving, indexing and reindexing content. The Ingest API will have
    not just the enrichment stages as a client, but also any BBC team that
    wishes to push its data directly to the search system already transformed.
    Received content will need to be archived in a ``raw'' form so that
    indexes can be reorganised and rebuilt if their structure need to change. It
    is also possible that the archived content might be repushed via the
    enrichment stages to take advantage of new business rules added therein by
    the previous subteam. There is also much work just around designing the
    structure of indexes, configuring linguistic matching and otherwise
    optmising retrieval that it might prove necessary to split out a subteam
    dedicated to those tasks.
  \item \textbf{Results Pages.} This is the subteam dedicated to the front
    end web pages. This is where user experience, design and other front
    end concerns are a primary focus. It is expected that this subteam
    will make requirements for the ingest subteam.
\end{itemize}

@@

The loose coupling afforded by linked data and REST should allow these areas
to evolve independently without changes causes breakages. For example, the
discovery component should be able to generate more linked data through finding
new ways of extracting metadata from content without the enrichment stage
suffering. This in contrast to more brittle RPC-over-HTTP architectures where
an upstream client sending a new XML or JSON format would cause a service to
start rejecting the requests unless the service was updated at the same time.

Introducing some devops responsibilities to the individual subteams and
making use of cloud technology could even permit each subteam to
develop their respective component(s) in different programming languages or
with different frameworks since the components only share information
via HTTP. These are decisions to be made by the developers as they come
to evaluate the best tools for their respective tasks.

>>>>

As depicted in figure~\ref{led-indexing-chain}, the architectural
approach is based around discrete, decoupled, RESTful services
forming a conceptual pipeline that takes notification of content
through a process of augmentation, validation and indexing. Recognising
and exploiting Conway's Law\cite{conway1968committees}, a good strategy
would be to focus subteams on each major area of the application
(so that the team organisation fits the architecture rather than the
architecture emerging from the team structure).

@@

\begin{itemize}
  \item \textbf{Discovery.} This subteam will focus on the URLNotification
    and URLFetch services as well as any integration work upstream to
    generate notifications where such mechanisms do not already exist for certain
    types of content. Typical considerations will be around RSS/Atom feeds that
    might notify of new content, message-based notifications from other
    systems and maintaining a crawler that finds the rest.
  \item \textbf{Enrichment and Inference.} Here the development team will focus
    on integration with BBC or external data sources to enrich information
    coming from the discovery stages. The developers will also need
    to gain sufficient domain knowledge of each content area to make sound
    inferences from the enriched metadata that then generate sensible
    values for fields required by the search indexes.
  \item \textbf{Ingest.} The Ingest API and the search indexes themselves
    will be maintained by a subteam responsible for accepting, validating,
    archiving, indexing and re-indexing content. The Ingest API will have
    not just the enrichment stages as a client, but also any BBC team that
    wishes to push its data directly to the search system already transformed.
    Received content will need to be archived in a ``raw'' form so that
    indexes can be reorganised and rebuilt if their structure need to change. It
    is also possible that the archived content might be re-pushed via the
    enrichment stages to take advantage of new business rules added therein by
    the previous subteam. There is also much work just around designing the
    structure of indexes, configuring linguistic matching and otherwise
    optimising retrieval that it might prove necessary to split out a subteam
    dedicated to those tasks.
  \item \textbf{Results Pages.} This is the subteam dedicated to the front
    end web pages. This is where user experience, design and other front
    end concerns are a primary focus. It is expected that this subteam
    will make requirements for the ingest subteam.
\end{itemize}

@@

The loose coupling afforded by linked data and REST should allow these areas
to evolve independently without changes causing breakages. For example, the
discovery component should be able to generate more linked data through finding
new ways of extracting metadata from content without the enrichment stage
suffering. This in contrast to more brittle RPC-over-HTTP architectures where
an upstream client sending a new XML or JSON format would cause a service to
start rejecting the requests unless the service was updated to understand these
new requests.

Introducing some devops\cite{huttermann2012devops}
responsibilities to the individual subteams and
making use of cloud technology could even permit each subteam to
develop their respective component(s) in different programming languages or
with different frameworks since the components only share information
via HTTP. These are decisions to be made by the developers as they come
to evaluate the best tools for their respective tasks.

### 2014-05-20 chapter5.3.tex
Done! Reviewed and ready to submit.

The BBC Search application differs somewhat from many other sites in that
the vast majority of the effort, complexity and codebase lives well
below the HTML/CSS/Javascript surface. The web application side follows
a typical stack comprising Javascript/CSS interface, server-side code/templates
to render the pages and a data layer (the search indexes). However, it has been
shown so far that there are orders of magnitude more complexity upstream
of this data layer, but I hope I have shown that linked data technologies
will reduce some of the unnecessary complexity at least.

This has implicates for planning features, stories, tasks, etc. within
an Agile methodology as the first story to display the most basically
functionality on a web page can easily lead to a wealth of engineering
behind the scenes. In this case, there are a lot of systems already in
place, so this road map will attempt to keep features as iterative as possible.

@@

\begin{figure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.42,options=-traw]
      \input{basic-ontology.dot}
    \end{dot2tex}
  \end{center}
  \caption{Basic ontology modelling the traditional ``title, link, description'' search result\label{fig:initial-ontology}}
\end{figure}

@@

There are modelling decisions still to be
made around whether to use this new vocabulary exclusively
or attempt to follow an existing one such as Schema.org. The
World Wide Web Consortium (W3C) usually recommends the practice
of \emph{extending} existing vocabularies over coining new
ones, but the linked data model always allows us to publish
mappings to existing vocabularies. However, small, bespoke
ontologies are arguably easier to define, control and iterate
in an agile manner and mappings to existing vocabularies
can be published later.

@@

The front end application can continue to search the
existing search indexes independant of any work being done
to improve the ingest chain. The importance of developing
this feature first is to ensure the information architecture
and domain models are defined up front. After this point,
the other subteams can proceed with the features below
while the results page developers keep iterating on
a user interaction that evolves through user testing and
feedback.

@@

The ``Ingest'' subteam needs to ensure the Ingest API can
accept content meeting the basic vocabulary outline in
figure~\ref{fig:initial-ontology}, validating ones
that do not contain the basic fields and evolve the API. If
the results page developers choose to alter the domain
model based on design iterations and user feedback, then
these changes can propogate back as requirements for the
content ingest.

@@

Elasticsearch is a standalone search server based on Apache Lucene
that can store, index and retrieve schemaless JSON structures.
The indexing chain is to deal with RDF graphs, for which JSON-LD
is a powerful JSON serialisation that can be sent to Elasticsearch
without any transformation.
A simple prototype of an ingest function written in Python
that receives JSON-LD is shown in listing~\ref{lst:ingest}.

\begin{lstlisting}[language=Python,label=lst:ingest]
from elasticsearch import Elasticsearch
import json

def ingest_jsonld(jsonld_string):
  body = {'jsonld': json.loads(jsonld_string)}
  ElasticSearch().index(
    index='search', body=body, doc_type='item')
\end{lstlisting}

@@

The \emph{Discovery} subteam will need to investigate
suitable mechanisms for notifying when certain programmes
objects have changed. There are asynchronous, message-based
systems in place witin the BBC specifically around
programmes change notifications and the engineered solution
is likely to make use of that.

Alongside this work, those responsible for enrichment and
inference will need to define (and apply) the rules for
mapping the vocabularies used by programmes microsites
to the ontology and vocabulary used in the search application.
Such rules will extend the form introduced in
section~\ref{sec:ld-indexing}.

@@

One difficulty is around
the temporal nature of programmes information. The graph
shown back in figure~\ref{question-time} shows
the time of the next broadcast, but that information will
soon expire and the search system might be interested in
reindexing that programme when the nature of its availability
on BBC iPlayer changes.

It is thus likely that the Discovery subteam working on the
URLNotification component will need to develop components
that query an archive of the linked data ingested to look
for items that may need reingested. They may need to
place requirements on the Ingest team to store an archive
of the linked data within a \emph{triple store} or other
data store (note that Elasticsearch has been known to be
suitable to act as both a search service and a NoSQL-style
document store in one). It is then a decision for teh
engineers as to whether complex SPARQL queries can mine
for programmes (or indeed any) content that has passed
a significant point of time at which the information becomes
out of date or whether to augment the simple ontology
in figure~\ref{fig:basic-ontology} with the concept of
a search result's information \emph{expiring} as shown in
figure~\ref{fig:expiring-ontology}.

\begin{figure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{expiring-ontology.dot}
    \end{dot2tex}
  \end{center}
  \caption{Concept of a potential search result's information expiring has been added}
  \label{fig:expiring-ontology}
\end{figure}

This expiry concept is not necessarily that the content item
should no longer appear in the search indexes, but that the
information should be considered stale and refetching the data
is recommended. This is not too far removed from Google
recrawling pages based on some assessment of how often the page
should be checked, but here we can use the semantic metadata
available publicly (and indeed internally) to get a more
precise idea of a good expiry date.

@@

\begin{figure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{recommended-ontology.dot}
    \end{dot2tex}
  \end{center}
  \caption{Ontology augmented with the concept of a recommended link for an entity}
  \label{fig:recommended-ontology}
\end{figure}

@@

The enrichment components could be extended to fetch additional
metadata by integrating against backend services that drive
these sites. Investigations will need to be made around this,
but any new information that can be added will be an improvement
over the current way the sites are simply web crawled and scraped.

>>>>

The BBC Search application differs somewhat from many other sites in that
the vast majority of the effort, complexity and codebase lives well
below the HTML/CSS/Javascript surface. The web application side follows
a typical stack comprising JavaScript/CSS interface, server-side code/templates
to render the pages and a data layer (the search indexes). However, it has been
shown so far that there are orders of magnitude more complexity upstream
of this data layer, but I hope I have shown that linked data technologies
will reduce some of the unnecessary complexity at least.

This has implications for planning features, stories, tasks, etc. within
an Agile methodology as the first story to display the most basically
functionality on a web page can easily lead to a wealth of engineering
behind the scenes. In this case, there are a lot of systems already in
place, so this road map will attempt to keep features as iterative as possible.

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}[scale=0.6,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{basic-ontology.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{Basic ontology modelling the traditional ``title, link, description'' search result\label{fig:initial-ontology}}
\end{figure}

@@

There are modelling decisions still to be
made around whether to use this new vocabulary exclusively
or attempt to follow an existing one such as Schema.org. The
World Wide Web Consortium (W3C) usually recommends the practice
of \emph{extending} existing vocabularies over coining new
ones, but the linked data model always allows us to publish
mappings to existing vocabularies. Small, bespoke
ontologies are arguably easier to define, control and iterate
in an agile manner and mappings to existing vocabularies
can be published later.

@@

The front end application can continue to search the
existing search indexes independent of any work being done
to improve the ingest chain. The importance of developing
this feature first is to ensure the information architecture
and domain models are defined up front. After this point,
the other subteams can proceed with the features below
while the results page developers keep iterating on
a user interaction that evolves through user testing and
feedback.

@@

The ``Ingest'' subteam needs to ensure the Ingest API can
accept content meeting the basic vocabulary outlined in
figure~\ref{fig:initial-ontology}, validating ones
that do not contain the basic fields. If
the results page developers choose to alter the domain
model based on design iterations and user feedback, then
these changes can propagate back as requirements for the
content ingest.

@@

Elasticsearch is a standalone search server based on Apache Lucene
that can store, index and retrieve schema less JSON structures.
The indexing chain is to deal with RDF graphs, for which JSON-LD
is a powerful JSON serialisation that can be sent to Elasticsearch
without any transformation.
A simple prototype of an ingest function written in Python
that receives JSON-LD is shown in listing~\ref{lst:ingest}.

\begin{lstlisting}[language=Python,label=lst:ingest,caption=Python code to index JSON-LD strings in Elasticsearch.]
from elasticsearch import Elasticsearch
import json

def ingest_jsonld(jsonld_string):
  body = {'jsonld': json.loads(jsonld_string)}
  ElasticSearch().index(index='search', body=body)
\end{lstlisting}

@@

The \emph{Discovery} subteam will need to investigate
suitable mechanisms for notifying when certain programmes
objects have changed. There are asynchronous, message-based
systems in place within the BBC specifically around
programmes change notifications and the engineered solution
is likely to make use of that.

The URLFetch component should be able to create an RDF graph
like that depicted in figure~\ref{question-time} by
fetching the microsite for the changed programme object
and parsing any RDFa and/or Microdata. In listing~\ref{lst:rdfa},
we can see this is achieved quite succinctly with the
RDFLib library's built-in support for metadata embedded within
HTML documents. The function takes any RDF graph (e.g. the minimal
graph shown in listing~\ref{lst:minimal}), attempts to look up
all subjects by their URI and adds any RDF metadata found.

\begin{lstlisting}[language=Python,label=lst:rdfa,caption=Use of RDFLib to deference all subjects in upstream graph far and add any linked data found.]
def fetch_metadata_about_subjects(graph):
  for subject in graph.subjects():
    graph.parse(str(subject))
\end{lstlisting}

Alongside this work, those responsible for enrichment and
inference will need to define (and apply) the rules for
mapping the vocabularies used by programmes microsites
to the ontology and vocabulary used in the search application.
Such rules will extend the examples introduced in
section~\ref{sec:ld-indexing}. A simple function that
uses \emph{RDFLib} and \emph{FuXi} Python libraries to infer
properties using a given rule set is shown in listing~\ref{lst:infer}.

\begin{lstlisting}[language=Python,label=lst:infer,caption=Python code to expand an RDFLib Graph with inferred properties using FuXi.]
from rdflib import Graph
from FuXi.Rete.RuleStore import SetupRuleStore
from FuXi.Rete.Util import generateTokenSet
from FuXi.Horn.HornRules import HornFromN3

def apply_inference_rules(graph, ruleset):
  rule_store, rule_graph, network \
    = SetupRuleStore(makeNetwork=True)
  closure_delta = Graph()
  network.inferredFacts = closure_delta
  for rule in HornFromN3(ruleset):
    network.buildNetworkFromClause(rule)

  network.feedFactsToAdd(generateTokenSet(graph))

  return graph + closure_delta
\end{lstlisting}

@@

One difficulty is around
the temporal nature of programmes information. The graph
shown back in figure~\ref{question-time} shows
the time of the next broadcast, but that information will
soon expire and the search system might be interested in
re-indexing that programme when the nature of its availability
on BBC iPlayer changes.

It is thus likely that the Discovery subteam working on the
URLNotification component will need to develop components
that query an archive of the linked data ingested to look
for items that may need re-ingested. They may need to
place requirements on the Ingest team to store an archive
of the linked data within a \emph{triple store} or other
data store (note that Elasticsearch has been known to be
suitable to act as both a search service and a NoSQL-style
document store in one). It is then a decision for the
engineers as to whether complex SPARQL queries can mine
for programmes (or indeed any) content that has passed
a significant point of time at which the information becomes
out of date or whether to augment the simple ontology
in figure~\ref{fig:initial-ontology} with the concept of
a search result's information \emph{expiring} as shown in
figure~\ref{fig:expiring-ontology}.

\begin{figure}[t]
  \begin{center}
    \begin{tikzpicture}[scale=0.6,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{expiring-ontology.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{Concept of a potential search result's information expiring has been added}
  \label{fig:expiring-ontology}
\end{figure}

This expiry concept is not necessarily that the content item
should no longer appear in the search indexes, but that the
information should be considered stale and re-fetching the data
is recommended. This is not too far removed from Google
re-crawling pages based on some assessment of how often the page
should be checked, but here we can use the semantic metadata
available publicly (and indeed internally) to get a more
precise idea of a good expiry date.

@@

\begin{figure}[t]
  \begin{center}
    \begin{tikzpicture}[scale=0.6,transform shape]
    \begin{dot2tex}[dot,pgf,codeonly]
      \input{recommended-ontology.dot}
    \end{dot2tex}
    \end{tikzpicture}
  \end{center}
  \caption{Ontology augmented with the concept of a recommended link for an entity}
  \label{fig:recommended-ontology}
\end{figure}

@@

The enrichment components could be extended to fetch additional
metadata by integrating against back-end services that drive
these sites. Investigations will need to be made around this,
but any new information that can be added will be an improvement
over the current way the sites are simply web crawled and scraped.

### 2014-05-20 chapter6.tex
Done! Reviewed and ready to submit.

The shift from enterprise integration to linked enterprise data
seems particulary suitable for the BBC given the legacy of
distinct data sources that has built up over time. It is hoped that
the search application can act as a strong example of the advatanges
of publishing enterprise data as linked data and that integration
costs can significantly reduce as a result.

@@

Future analysis is recommended to address auxillary features such as
the autocomplete\cite{morville2010search} feature that appears when a user
is typing in
the search box. Much of this data is manually-maintained as is the case
with Editor's Choice. Future work should be able to look into a suitable
combination of automatic inference and manual curation to collate
possible autocomplete or autosuggest searches and links with the need to
maintain the whole list of potential completions by hand. This should follow
naturally from the work on Editor's Choice, but the autocomplete
improvements should
be designed after any lessons are learnt from the Editor's Choice development.

@@

Further studies, analsys and proposals after implementations of this proposal
are recommended to investigate the benefits of linking more data
between the content on different BBC sites.

>>>>

The shift from enterprise integration to linked enterprise data
seems particularly suitable for the BBC given the legacy of
distinct data sources that has built up over time. It is hoped that
the search application can act as a strong example of the advantages
of publishing enterprise data as linked data and that integration
costs can significantly reduce as a result.

@@

Future analysis is recommended to address auxiliary features such as
the autocomplete\cite{morville2010search} feature that appears when a user
is typing in
the search box. Much of this data is manually-maintained as is the case
with Editor's Choice. Future work should be able to look into a suitable
combination of automatic inference and manual curation to collate
possible autocomplete or autosuggest searches and links with the need to
maintain the whole list of potential completions by hand. This should follow
naturally from the work on Editor's Choice, but the autocomplete
improvements should
be designed after any lessons are learnt from the Editor's Choice development.

@@

Further studies, analysis and proposals after implementations of this proposal
are recommended to investigate the benefits of linking more data
between the content on different BBC sites.
